---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# mix-fdr

<!-- badges: start -->
<!-- badges: end -->

The project `mix-fdr` is the final project of MATH 5472. It aims to investigate mixfdr, an empirical Bayes method for estimating fdr and effect size simultaneouly purposed by this paper: *Omkar Muralidharan. An empirical bayes mixture method for effect size and false discovery rate estimation. Ann. Appl. Stat. 2010.*


## Enviromnent

The R code is developed in R version 4.0.2. 
```{r}
sessionInfo()
```

To run the simulation code, we first need the following packages that provide various empirical Bayes method.

```{r, eval=FALSE}
install.packages("locfdr")
install.packages("EBayesThresh")
```
Package `spline` may also need to be loaded before running the simulation code.

## Content of codes
* `mixfdr_fun.R`: containts various functions that implemented the mixfdr algorithm
* `sim_fdr.R`: produce the fdr estimation results in section 2.2 of the report
* `sim_effect_sz.R`: produce the effect sise estimation resluts in section 2.1 of the report.

## Running simulation code

### Effect size estimation

To reproduce the Figure 1 in the report, we can source the `sim_effect_sz.R` directly

```{r, eval=FALSE}
source("sim_effect_sz.R")
```

### Fdr estimation

To reproduce Figure 2, 3, we need to set different values on `N_null` in the `sim_fdr.R`

* `N_null = 50` : the original setting in the paper, corresponds to figure 2
* `N_null = 100` : the dense setting on effect size, correspondd to figure 3

Then source the script. A small example is that when we set the follwing parameters in the code
```{r, eval=FALSE}
n_rep = 100
N = 1000
N_null = 100
J = 3
```

The code will output the Figure 3 in the report:
```{r, plot-fdr, warning=FALSE}
source("sim_fdr.R")
```



